Surveillance systems play a crucial role in enhancing public safety and security measures. However, the effectiveness of these systems is often hindered by the poor quality of video footage, particularly when it comes to recognizing individuals of interest. Low-resolution cameras, suboptimal lighting conditions, and other environmental factors can result in captured video data that lacks the necessary clarity and detail required for accurate face recognition. This limitation poses significant challenges in investigations or situations where identifying individuals from surveillance footage is essential.
To address this issue, this project aims to develop an effective pipeline for face detection, extraction, and enhancement to improve the visual quality of faces in video data. The YOLOv8 object detection model is employed to localize human keypoints within the video frames, enabling the extraction of face bounding boxes based on the detected facial keypoints. To improve the visual quality and resolution of the extracted face images, several upsampling and super-resolution techniques are explored. Initially, conventional upsampling methods are utilized. Furthermore, an advanced approach leveraging the Image Super Resolution using Enhanced Super-Resolution Generative Adversarial Networks (ESRGAN) is integrated to potentially improve the visual quality and resolution of the extracted face images. Experimental results indicate that while the ESRGAN model achieves impressive upscaling and enhancement for face images of sufficient resolution, its performance is limited when applied to low-resolution face bounding boxes extracted from videos with poor visual quality. The proposed pipeline demonstrates the potential for automated face extraction and enhancement from video data, highlighting the challenges and considerations involved in real-world applications.\\

\textbf{Index words - Face Detection, Computer Vision, Human Keypoint Detection (YOLOv8 Pose Detection Model), Image Super-Resolution using ESRGAN implementation\\}
