\documentclass[12pt]{article}

\input{1_header/packages.tex}

\begin{document}
\restoregeometry

\setcounter{tocdepth}{5}

\input{1_header/firstpage.tex}
\pagebreak

\input{1_header/secondpage.tex}
\pagebreak

\input{1_header/thirdpage.tex}
\pagebreak

\input{1_header/fourthpage.tex}
\pagebreak

\input{1_header/fifthpage.tex}
\pagebreak

\tableofcontents
\pagebreak

\listoffigures
\pagebreak

\justify
\section*{\textlarger[2]{Abstract}}
\input{1_header/abstract.tex}
\pagebreak

\section{\textlarger[2]{Introduction}}
\input{1_header/introduction.tex}
\pagebreak

\section{\textlarger[2]{Literature Review}}
\input{2_body/literature.tex}
\pagebreak

\section{\textlarger[1.5]{Methodology}}
\input{2_body/methods.tex}
\pagebreak

% \section{\textlarger[1.5]{Implementation results}}
\input{2_body/implementation.tex}
\pagebreak

\section{\textlarger[1.5]{Results and discussion}}
\input{2_body/results.tex}
\pagebreak

\section{\textlarger[1.5]{Conclusions}}
\input{2_body/conclusions.tex}
\pagebreak

\section{\textlarger[1.5]{Future Scope}}
\input{2_body/futuregoals.tex}
\pagebreak

\section{\textlarger[1.5]{References}}
\printbibliography[heading=none]
\begin{thebibliography}{9}

\bibitem{Yolov8:2024:PoseEstimation}
Ultralytics. (n.d.). Pose Estimation. Retrieved from <https://docs.ultralytics.com/tasks/pose/>

\bibitem{Ultralytics:2024:PoseDatasets}
Ultralytics. (n.d.). Pose Datasets Overview. Retrieved from <https://docs.ultralytics.com/datasets/pose/>

\bibitem{TensorFlowHub:2024:ESRGAN}
TensorFlow Hub. (n.d.). Image Super Resolution using ESRGAN TensorFlow Hub. Retrieved from https://www.tensorflow.org/hub/tutorials/image enhancing

\bibitem{ESRGAN:2024:NetworkArchitecture}
ESRGAN. (n.d.). Network Architecture. Retrieved from https://esrgan.readthedocs.io/en/latest/pages/esrgan.html - network-architecture

\bibitem{TensorFlowHub:2023:ESRGAN}
TensorFlow Hub. (n.d.). ESRGAN. TensorFlow Hub. Retrieved from https://tfhub.dev/tensorflow/esrgan x4/1

\bibitem{Zhang:2020:ISR:3373121.3373134}
Zhang, Y., Liu, X., and Wang, Z., 2020, Image Super-Resolution using Enhanced Super-Resolution Generative Adversarial Networks, arXiv preprint arXiv:2004.05983.
\end{thebibliography}

\end{document}
